Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2022-09-25 Documents/Paper/paper.Rnw
add affiliation
update paper

\author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
\affiliation{$^1$Department of Developmental Psychology and Socialization, University of Padova\\
$^2$UNIMI TODO }

@@

<<settings, echo=FALSE, message=FALSE>>=
library(kableExtra)
library(ggplot2)

@@

# Chunk theme
thm=knit_theme$get("bclear")
knitr::knit_theme$set(thm)
knitr::opts_chunk$set(background = c(.98, .98, 1))

@@

devtools::load_all("../../")
source("../Utils_report.R")

@@

drake_load_paper()
@

>>>>

\author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
\affiliation{$^1$Department of Developmental Psychology and Socialization - University of Padova\\
$^2$Department of Psychology - University of Milano-Bicocca}

@@

<<settings, echo=FALSE, message=FALSE, include=FALSE>>=
library(kableExtra)
library(ggplot2)

@@

# # Chunk theme
thm=knitr::knit_theme$get("bclear")
knitr::knit_theme$set(thm)
knitr::opts_chunk$set(background = "#FAFAFF")

@@

devtools::load_all("../../")

@@

tar_load_paper(store = "../../Analysis/_targets/")
@
